\begin{rubric}{Work Experience}

\entry*[08/2017 -- 02/2018]%
        \textbf{VNPT Data Corporation} - \textbf{IT intern}        
	\begin{itemize}
        \item \textbf{Radius access control}\par
	Worked as IT intern in VNPT DATA corporation, Da Nang as part of the Hue University of Science internship program. Researching radius access control and managing local wifi network with Freeradius and Daloradius.
   \end{itemize}

\entry*[09/2018 -- 08/2020]%
        \textbf{Hanoi University of Science and Technology} - \textbf{Master student}        
	\begin{itemize}
        \item \textbf{Person re-identification}\par
	Participated in research projects related to computer vision with researchers at
MICA International Research Institute.
        \item Researching about machine learning and computer vision solutions for person
re-identification problem.
        \item Applying machine learning algorithms to propose a method for improving the
person re-identification problem's performance.
   \end{itemize}

\entry*[03/2021 -- 08/2024]%
        \textbf{Chonnam National University} - \textbf{PhD student}        
	\begin{itemize}
        \item \textbf{Rapid Response System (RRS)}\par
	Participated in RRS projects which is a research collaboration between Professors of the Artificial Intelligence department and doctors of Chonnam National University Hospital.     \begin{itemize}
	    \item This project develops a deep learning application system to improve performance in hospital emergency care.
            \item Author of Temporal Variational Autoencoder Network (TVAE) for In-hospital clinical emergency prediction (source: \url{https://github.com/nghianguyen7171/TVAE-RRS}). 
            \item Author of Multi-Gradient Siamese Temporal Network (MG-SiameseTS) for the Prediction of Clinical Events in Rapid Response Systems (source: \url{https://github.com/nghianguyen7171/new_mgsiameseTS}). 
            \item Author of Explainable Deep Contrastive Federated Learning System (Deep-CFL) for early prediction of clinical Status in-intensive Care Unit (ICU)).
	\end{itemize}
        
        \item \textbf{Fashion Recognition and Recommendation system}\par
        Proposed Fashion Recognition and Recommendation system (source: \url{https://github.com/nghianguyen7171/Fashion-Recognition-and-Recommendation-system})

        \item \textbf{Korean Emotion Recognition Challenge 2021 (KERC)}\par
        Proposed Emotion Recognition system for KERC 2021 challenge (source: \url{https://github.com/nghianguyen7171/KERC2021})

        \item \textbf{Aquaculture Artificial Intelligence Idea Contest}\par
        Proposed Food-organism utilization throughout the AI-based aquaculture industry (source: \url{https://github.com/nghianguyen7171/aquaculture_ai_contest_public})
   \end{itemize}

\end{rubric}